Fast-Match:\\Fast and Robust Feature Matching on Large Images

### 2014-06-19 paper.tex
Updated caption for timings figure

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{Running times of different variations of \emph{Fast-Match} and \emph{Ratio-Match}. The top plot shows results for two 10~MPixel images two 3~Mpixel images is used for the comparison at the bottom. From the left, the first two results presume a precached image while the rest do not require knowing any inputs beforehand. The image pairs used be seen in Figure~\ref{fig:match_example}.}
    \label{fig:timings}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{Running times of different variations of \emph{Fast-Match}
    and \emph{Ratio-Match}. The left plot shows results for two 3~Mpixel
    images while the plot on the right shows results for two 10~Mpixel
    images. The two leftmost results in either plot presume a precached
    image while the rest require no caching. The image
pairs used can be seen in Figure~\ref{fig:match_example}.}
    \label{fig:timings}
\end{figure}
